Demonstration of matching route networks

### 2024-04-18 r/README.qmd
Update README

```{r}
list.files("data-raw/geojson")
# File is in rnetmatch/r/inst/extdata/princes_street_minimal.geojson
f = 
x = sf::read_sf("inst/extdata/princes_street_minimal_x_1.geojson")
x = x |> sf::st_transform("EPSG:27700")
y = sf::read_sf("inst/extdata/princes_street_minimal.geojson")
y = y |> sf::st_transform("EPSG:27700")
```

@@

```{r}
matched_df = rnet_match(x, y, dist_tolerance = 20, angle_tolerance = 0.1, trees = "xy")
y_to_match = y |>
  transmute(j = 1:n(), value) |>
  sf::st_drop_geometry() 
matched_df_y = left_join(matched_df, y_to_match)
x$length_x = sf::st_length(x) |>
  # Drop units:
  units::drop_units()
x_to_match = x |>
  transmute(i = 1:n(), length_x) |>
  sf::st_drop_geometry()
matched_df_xy = left_join(matched_df_y, x_to_match)
x_formula = matched_df_xy |>
  mutate(value_formula = value * shared_len / length_x)
x_formula
x_with_values = x_formula |>
  group_by(id = i) |>
  summarise(
    value = sum(value_formula),
    length_x = first(length_x)
    )
x_joined = left_join(x, x_with_values)
```

@@

```{r}
total_distance_y = sum(as.numeric(y$value * sf::st_length(y)))
```

>>>>

```{r}
list.files("data-raw/geojson")
x = sf::read_sf("inst/extdata/princes_street_minimal_x_1.geojson")
x = x |> sf::st_transform("EPSG:27700")
y = sf::read_sf("inst/extdata/princes_street_minimal.geojson")
y = y |> sf::st_transform("EPSG:27700")
```

@@

```{r}
nrow(x)
nrow(y)
matched_df = rnet_match(x, y, dist_tolerance = 20, angle_tolerance = 20, trees = "xy")
nrow(matched_df)
matched_df
length_x = sf::st_length(x) |>
  # Drop units:
  units::drop_units()
length_x

y_to_match = y |>
  transmute(j = 1:n(), value) |>
  sf::st_drop_geometry() 
matched_df_y = left_join(matched_df, y_to_match)
x_to_match = x |>
  transmute(i = 1:n(), length_x) |>
  sf::st_drop_geometry()
matched_df_xy = left_join(matched_df_y, x_to_match)
x_formula = matched_df_xy |>
  mutate(value_formula = value * shared_len / length_x)
x_formula
x_with_values = x_formula |>
  group_by(id = i) |>
  summarise(
    value = sum(value_formula),
    length_x = first(length_x)
    )
x_joined = left_join(x, x_with_values)
```

@@

```{r}
total_distance_y = sum(as.numeric(y$value * sf::st_length(y)))
total_distance_y
```
